### 2014-02-11 docs/reports/finalreport/report.tex
adding significance test results

\maketitle
\begin{abstract}
The report explains the details of design and developing process of a translator retrieval platform. The platform's objective is to suggest an appropriate translator to a client. It manages the process of translation until the last step. Additionally, by providing a translation memory system translators can exploit their previous translated texts in their new ones. C\texttt{\#}.NET and MS SQL SERVER are used as main platform and Lucene.NET is the text processor. The system is designed based on Data Driven Design (DDD) model. Windows Azure is the deployment environment.
\end{abstract}

@@

\input{introduction}
\newpage
\input{problem}
\newpage
\input{architecture}
\newpage
\input{design}
\newpage
\input{development}
\newpage

>>>>

\maketitle
\begin{abstract}
The report explains the details of design and develop of a translator retrieval platform. The platform's objective is to suggest an appropriate translator to a client. It manages the process of translation until the last step. Additionally, by providing a translation memory system translators can exploit their previous translated texts in their new ones. C\texttt{\#}.NET and MS SQL SERVER are used as main programming platforms and Lucene.NET is the text processor. The system is designed based on Data Driven Design (DDD) model. Windows Azure is the deployment environment.
\end{abstract}

@@

\input{introduction}
\input{problem}
\input{architecture}
\input{design}
\input{development}

### 2014-02-11 docs/seminar/evaluation.tex
adding significance test results

The calculation is done based on $181$ records of purchased orders. The coefficient values of applying Pearson Correlation ($r$) and Spearman's Rank Order Correlation ($r_s$) are shown in Table \ref{table:Spearman}. TODO: Significance Test .

The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers. Nevertheless among the introduced algorithms, $GP2$ outperforms the others. In comparison to $Top1$, $Top5$ has slightly better performance. The results are also nearly the same when comparing based on language-pairs.

\begin{table}
\begin{center}
\scalebox{1.2}{
\begin{tabular}{p{1cm}|c|c|c|}
\cline{2-4} & Top1 & Top5 & GP2  \\
\hline \multicolumn{1}{ |c| }{$r$} & 0.018 & 0.063 & 0.117\\
\hline \multicolumn{1}{ |c| }{$r_s$} & 0.052 & 0.087 & 0.145\\
\hline
\end{tabular}
}
\caption{Comparison between algorithms and feedbacks}
\label{table:Spearman}
\end{center}
\end{table}

>>>>

In order to calculate the correlation value, we applied Spearman Rank Order and Kendall Rank Correlation as two common methods. Table \ref{table:correlation} shows the results of Spearman correlation coefficient ($r_s$) and Kendall's tau coefficient ($\tau$) using $181$ records of purchased orders. Table \ref{table:signtest} represents the Significance Test of both methods calculated by R.

As it is usual in many cases, the coefficient value of Spearman is slightly higher than Kandell's. The outcome shows an approximately weak correlation between aggregation functions and feedbacks of proof-readers. TODO about significance test??.

Comparing the algorithms, $GP2$ outperforms the others in both correlation tests. In comparison to $Top1$, $Top5$ has slightly better performance. The results are also nearly the same when comparing based on language-pairs.

\begin{table}
\begin{center}
\scalebox{1.2}{
\begin{tabular}{p{1cm}|c|c|c|}
\cline{2-4} & Top1 & Top5 & GP2  \\
\hline \multicolumn{1}{ |c| }{$r_s$} & 0.052 & 0.089 & 0.145\\
\hline \multicolumn{1}{ |c| }{$\tau$} & 0.034 & 0.059 & 0.102\\
\hline
\end{tabular}
}
\caption{Correlation Test Between Algorithms and Proof-readers' Feedbacks}
\label{table:correlation}
\end{center}
\end{table}

\begin{table}
\begin{center}
\scalebox{1.2}{
\begin{tabular}{p{1cm}|c|c|c|}
\cline{2-4} & Top1 & Top5 & GP2  \\
\hline \multicolumn{1}{ |c| }{$r_s$} & 0.4866 & 0.2295 & 0.05038\\
\hline \multicolumn{1}{ |c| }{$\tau$} & 0.5157 & 0.2562 & 0.05263\\
\hline
\end{tabular}
}
\caption{P-Value of Significance of Correlation Test Algorithms}
\label{table:signtest}
\end{center}
\end{table}
